---
title: "Martinez"
author: "Marine Martinez"
format: html
---
```{r}
library(vroom)
library(here)
library(dplyr)
library(tidyr)
library(ggplot2)
here::i_am("grades-test.Rproj")
```
##Question 1 Load the data set.
```{r}
grades <- vroom(here("grades.csv"))
```
## Question 2 Give the number of grades in the data set directly in the text of your quarto file, in a sentence of the form “The data set contains xxx grades.” where xxx is replaced by the number of grades. This must be computed from the data set.
The data set contains 68018 grades.

## Question 3: Use distinct() compute the number of students on the data set and report the value directly in the text as in the previous question.
```{r}
#| echo: false
grades|>
  distinct(id)|>
  summarise(n())
```
The number of student is 962. 

## Question 4: Create a students data frame that contains one row per student and two variables, id and group that gives the assignment of each student to their group. Make sure that each student appears on only once in the data frame. Include a short extract of the data frame in the quarto rendering.
```{r}
grades|>
  distinct(id, group)|>
  slice_sample(n=5)|>
  knitr::kable()
```
## Question 5 Use a graphical representation to display the number of students per group.
```{r}
grades |>
  distinct(id, group)|>
  group_by(group)|>
  summarise(nb=n())|>
  mutate(group = factor(group, ordered = TRUE, levels = 1:20))|>
  ggplot(aes(x=group, y=nb))+
  geom_col()+
  xlab("Group")+
  ylab("Number")+
  ggtitle("Distribution of students in groups")
```
##Question 6: Compute the average of all the grades in Spirituality and Rituals in each group and display graphically this average as a function of the group. It is recommend to use geom_col() for this task (read the documentation!).
```{r}
library(stringr)
grades |>
  filter(str_detect(course,"Spirituality and Rituals"))|>
  group_by(group)|>
  summarise(Mean=mean(grade))|>
  mutate(group = factor(group, ordered = TRUE, levels = 1:20))|>
  ggplot(aes(x=group, y=Mean, fill=group))+
  geom_col()+
  xlab("Group")+
  ylab("Mean")+
  ggtitle("Distribution of mean in groups")
```

## Question 7 Compare graphically the distribution of the grades of the 2 semesters.
```{r}
grades |>
  mutate(semester = factor(semester, ordered = TRUE, levels = 1:2))|>
  ggplot(aes(x=grade, y=semester, fill=semester))+
  geom_boxplot()+
  xlab("Grade")+
  ylab("Semester")+
  ggtitle("Distribution of grades between semester")
```
## Question 8 Compute the number of grades per student and include in your quarto rendering an extract of the resulting data frame. Make sure to keep in the data frame the id of the students but also their group. Include in the text a markdown table with the minimum, maximum, average and median number of grades per student.
```{r}
grades|>
  group_by(id, group)|>
  summarise(nb_grades= n(), .groups= "drop")|>
  slice_sample(n=5)|>
  knitr::kable()
```
```{r}
#| echo: false
grades|>
  group_by(id)|>
  summarise(max =max(grade),
            median= median(grade),
            min= min(grade),
            mean(grade))|>
  slice_sample(n=5)
```
| id | max |median|min  |mean |
|----|-----|------|-----|------|
| 480|  19 | 9,50 | 3.0 | 10.07
| 277| 16.5| 18.5| 3.0  | 9.6|
| 565| 18.5| 10.70| 3.0| 10.8|
| 841| 17.3| 9.9| 5.5| 10.5|
| 774| 17 | 9.45| 3.0 | 9.5|

